Verifying Demonstrations

### 2017-10-09 protocol.tex
Adds individual verif and receipt freeness to protocol

If the proofs are stored publicly, then an individual can check that their proof 
has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.

\dots

Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
Alice has created one of the proofs.

Say that Alice submits her proof and stores the hash of the head of the 
\ac{tposet} after her proof is included.
Now she can remove her proof and just keep the hash to verify that her proof is 
still there.
She can also remove her signature key, so that Eve cannot use it to reproduce 
the signature using the same inputs.

>>>>

The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
an adversary from dropping participation proofs.
Thus each protester must verify that their own proof is indeed included.
This can be accomplished as follows.
After Alice commited to her proof (share) in the blockchain, she stores the hash 
of the block.
At a later time, she can still verify that the block is indeed still there.
At this point, this hash value is the only thing she must store for individual 
verifiability.

More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
must remove her secret PRF key, \(k_A\).
With this key Eve can verify that Alice has submitted a proof by computing 
\(pid'\gets PRF_{k_A}(cid)\) and compare \(pid = pid'\).
